Random Forest to find the top important features

### 2019-11-03 scripts/01_clean_pheno.Rmd
update

# below is for CRS only
samps <- read_csv('../data/cleaned_pheno/MRN_sampleid.txt', col_types = 'cc') %>% 
  left_join(tox_CRS, by  = 'MRN') %>% 
  filter(sampleid %in% pheno$Sampleid) %>% 
  # really mad that i have to remove some records in this way
  mutate(stop = replace(stop, MRN == '35546332' & grade == '0', '2018-01-30')) %>% 
  arrange(desc(stop)) %>% 
  distinct(sampleid, .keep_all = T)

# 35546332 has both None and grade 1 for CRS
# based on the date choose the 0
# choose the latest date grade for 00332772 : 1
# choose the latest date grade for 35546332 : 0
```

>>>>

# below is for CRS only
samps <- read_csv('../data/cleaned_pheno/MRN_sampleid.txt', col_types = 'cc') %>% 
  left_join(tox_CRS, by  = 'MRN') %>% 
  filter(sampleid %in% pheno$Sampleid) %>% 
  # really mad that i have to remove some records in this way
  mutate(stop = replace(stop, MRN == '35546332' & grade == '0', '2018-01-30')) %>% 
  arrange(desc(stop)) %>% 
  distinct(sampleid, .keep_all = T) %>% 
  rename(CRS_grade = grade) %>% 
  select(-stop)

# 35546332 has both None and grade 1 for CRS
# based on the date choose the 0
# choose the latest date grade for 00332772 : 1
# choose the latest date grade for 35546332 : 0

samps %>% 
  write_csv('../data/cleaned_pheno/cleaned_CRS.csv')
```

### 2019-11-03 scripts/15_RF_find_top_features.Rmd
clean the fucking toxicity grade var
update

>>>>

### Use the toxicity grade

```{r}
crs <- read_csv('../data/cleaned_pheno/cleaned_CRS.csv')

pheno <- pheno %>% 
  full_join(crs %>% 
              select(Sampleid  = sampleid, CRS_grade), by = 'Sampleid') %>% 
  mutate(CRS_grade = factor(CRS_grade))

all.equal(rownames(s_tb_rf), pheno$Sampleid)

########################################################################################

# what if just do as Tsoni says that classify 0 and 1 as N the other as Y
pheno <- pheno %>% 
  mutate(tox_crs = factor(if_else(as.character(CRS_grade) %in% c('0','1'), 'NO', 'YES')))

# select the 18 features that have > 95% relab
s_sum_top <- quantile(s_sum, 0.95)
combined_fil <- cbind(s_tb_rf[,names(s_sum[s_sum > s_sum_top])], pheno %>% 
                    select(tox_crs, ORR, Disease_Status_CAR))

dim(combined_fil)

CRS_RF <- randomForest(formula = tox_crs ~ ., data = combined_fil,  importance = T )

CRS_RF  %>% 
  pluck('err.rate') %>% 
  as.data.frame() %>% 
  mutate(ntree = seq(1, nrow(.))) %>% 
  gather(key = 'type', value = 'ERR', 'OOB':'YES') %>% 
  ggline(x = 'ntree', y = 'ERR', color = 'type', palette = 'lancet') +
  labs(x = 'Number of trees', 
       y = 'Error rate')

CRS_RF    # very high error rate. not working. 
```
